Interpretable Machine Learning for Science \\ with PySR and SymbolicRegression.jl

### 2023-05-01 src/tex/ms.tex
Put back stamp and put in center
Reference figures

\titlehead{
  \parbox{\textwidth}{
    \emph{PySR \& SymbolicRegression.jl}
    \hfill
    \giturl
  }
}

@@

Pseudocode for the main loop of \pysr is given in \cref{alg:pysr}.
\Cref{alg:evolve} gives pseudocode for the main \textit{evolve-simplify-optimize loop}.
\Cref{alg:mutate} outlines the set of mutations, supplemented with simulated annealing.
Finally, \cref{alg:tournament} describes the tournament selection strategy.

>>>>

\titlehead{
    \begin{center}
    \parbox{0.3\textwidth}{
        \hfill
        \emph{PySR \& SymbolicRegression.jl}
    }
    \hspace{2in}
    \parbox{0.3\textwidth}{
        \giturl
        \hfill
    }
    \end{center}
}

@@

Pseudocode for the outer loop loop of \pysr is given in \cref{alg:pysr}, which includes the migration steps shown in \cref{fig:migration}.
\Cref{alg:evolve} gives pseudocode for the main \textit{evolve-simplify-optimize loop}, formalizing parts of the cartoon in \cref{fig:evolution_loop}.
\Cref{alg:mutate} outlines the set of mutations, supplemented with simulated annealing.
Finally, \cref{alg:tournament} describes the tournament selection strategy.
